Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2014-11-21 manuscript.tex
Divide figure using dist to center of tesseroid
Matches the latest change in Tesseroids.

%\documentclass[paper,twocolumn]{geophysics}
\documentclass[manuscript]{geophysics}
%\documentclass[manuscript,endfloat]{geophysics}
\usepackage{graphicx}
\usepackage{amsmath}
\newcommand{\mitbf}[1]{\mathbf{{#1}}}

@@

These functions require three \texttt{GLQ} structures with roots scaled to the
integration limits $[\lambda_1, \lambda_2], [\phi_1, \phi_2], [r_1, r_2]$
(see equations~\ref{eq:tesspot}-\ref{eq:tesstensor}).

The integration consists of three \texttt{for} loops: one for longitude, one
for latitude, and one for radius.

@@

The adaptive discretization algorithm of \citet{Li2011} recursively
divides a tesseroid.

@@

>>>>

\documentclass[paper,twocolumn]{geophysics}
%\documentclass[manuscript]{geophysics}
%\documentclass[manuscript,endfloat]{geophysics}
\usepackage{graphicx}
\usepackage{amsmath}
\newcommand{\mitbf}[1]{\mathbf{{#1}}}

@@

These functions require three \texttt{GLQ} structures that contain the roots
and weights for GLQ integration in the three dimensions.

The roots must be scaled to the
integration limits $[\lambda_1, \lambda_2], [\phi_1, \phi_2], [r_1, r_2]$
(see equations~\ref{eq:tesspot}-\ref{eq:tesstensor}).

The integration consists of three \texttt{for} loops that sum the weighted
kernel functions evaluated at each GLQ point mass (the scaled roots).

@@

The adaptive discretization algorithm of \citet{Li2011}
divides a tesseroid recursively.

@@

UPDATE THE EQUATION TO THE CENTER OF THE TESSEROID + NUMBER OF DIVISION IN
EXAMPLE FIGURE.
